---
title: "fastablast: functions for Mothur fasta files and BLAST"
output: 
  html_document:
    keep_md: yes
author: "Marcus W. Beck, beck.marcus@epa.gov"
---

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/fawda123/fastablast?branch=master&svg=true)](https://ci.appveyor.com/project/fawda123/fastablast)
[![Travis-CI Build Status](https://travis-ci.org/fawda123/fastablast.svg?branch=master)](https://travis-ci.org/fawda123/fastablast)

This is the development repository for the fastablast package. Functions within this package can be used to format [Mothur](https://www.mothur.org/) fasta files for use with Blast and retrieval of information from [Blast](https://blast.ncbi.nlm.nih.gov/Blast.cgi) output files.

## Installing the package

The development version of this package can be installed as follows:

```{r eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('fawda123/fastablast')
library(fastablast)
```
```{r eval = T, echo = F, results = F, message = F}
devtools::load_all()
```

## Using the functions

Format a fasta file for BLAST with `formfst`:

```{r}
# path to input file
flin <- 'inst/fst_ex.fasta'

# execute
formfst(flin)
```

Save the file:

```{r, eval = F}
# file name
flout <- 'out.txt'

# execute
formfst(flin, flout)
```

Retrieve relevant info from BLAST file with `formbls`:

```{r}
# path to input file
flin <- 'inst/bls_ex.txt'

# execute
formbls(flin)
```

Save the file:

```{r, eval = F}
# file name
flout <- 'out.txt'

# execute
formbls(flin, flout)
```

